Best Practices for Developing Monte Carlo Methodologies in Molecular Simulations [Article v\versionnumber]

### 2025-06-06 paper/paper.tex
Updating the orientation test for two orthogonal vectors

\begin{figure}
\lstinputlisting[
language=Python,
label={sim:orientation_trials},
  caption={MC simulation of a single rigid body in three dimensions using Python 3 using $5\times 10^5$ random angular displacements with $\delta\theta_{max}=\pi/10$. Angle distributions were computed over $300$ equally-spaced bins with $20$ independent simulations (totaling $10^7$ orientations) to compare against theoretical expectations with approximately 68 \% of the distribution within one standard deviation.}
]{../codes/orientation_trials.py}
\end{figure}

@@

\begin{figure}
\lstinputlisting[
language=Python,
label={sim:rotationmatrix},
caption=The rotation\_matrix module generates a rotation matrix from an axis and angle.
]{../codes/rotation_matrix.py}
\end{figure}

>>>>

\begin{figure}
\lstinputlisting[
language=Python,
label={sim:orientation_trials},
  caption={MC simulation of a single rigid body in three dimensions using Python 3 using $5\times 10^5$ random angular displacements with $\delta\theta_{max}=\pi/10$. Angle distributions were computed over $300$ equally-spaced bins with $20$ independent simulations (totaling $10^7$ MC trials) to compare against theoretical expectations with approximately 68 \% of the distribution within one standard deviation.}
]{../codes/orientation_trials.py}
\end{figure}

@@

\begin{figure}
\lstinputlisting[
language=Python,
label={sim:rotationmatrix},
caption=The rotation\_matrix module generates a rotation matrix from an axis and angle.
]{../codes/rotation.py}
\end{figure}
